Consumer extinctions constrain phenotypic evolution in the resulting food web

### 2019-05-21 analyses/reproduce_analyses.Rmd
update analyses folder.

---
title: "Consumer extinctions constrain phenotypic evolution in the resulting food web"
subtitle: "Supplementary information"
author: "Code author: Matthew A. Barbour"
date: "`r Sys.Date()`"
output: 
  tufte::tufte_html:
    toc: true
#fontsize: 11pt
---

This document presents a hybrid summary of the code used to reproduce these analyses. It is intended to give the reader a higher-level picture of the analyses, but does not display more minor code related to aesthetics. The underlying code for this document is provided in *reproduce_analyses.Rmd* and is available at https://github.com/mabarbour/complexity_selection.

@@

Set number of bootstrap replicates for analyses and plots.

```{r set parameters, echo=TRUE}
n_boots_analysis <- 1000
n_boots_plots <- 100
```

```{r color palette}
# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
# order: orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
complex_color <- cbPalette[6] 
simple_color <- cbPalette[5] 
treatment_colors <- c(complex_color, simple_color)
```

@@

  # eliminate unknown sources of mortality
  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% 
  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% 
  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"), # rename Treatment to match presentation in manuscript
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber. I set these to 1 to permit an analysis with a binomial model.

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))

@@

We used graphical checks to evaluate whether our transformations of trait values resulted in a multivariate normal distribution. The histograms below show that our transformations resulted in approximately normal distributions for each phenotypic trait. Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line, suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.

@@

```{r Multivariate_QQ, fig.show = 'asis', fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
```

## Selection surfaces on gall midges: food-web treatments

We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival. The resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments. For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.

@@

We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.

```{r Bootstrap food-web model, cache=TRUE, echo=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

In order to reliably quantify linear trait-fitness relationships, we remove all higher-order terms from the model [Stinchcombe et al. 2008](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x).

@@

And refit using parametric bootstrapping.

```{r Bootstrap linear food-web model, cache=TRUE, echo=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

Chamber diameter, but not the other phenotypes, could be influenced by parasitism itself rather than being under natural selection. To estimate this potential bias, we subset our data to only include multi-chambered galls where there was variability in larval survival. We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in selection surface of chamber diameter in each food-web treatment.")
```

We gather regression coefficients from the full and reduced model to display trait-fitness relationships. For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship. <!--We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).-->

```{r Food-web alpha coefficients}
foodweb_bind <- bind_cols(
  as_tibble(boot_linear_foodweb_model$t),
  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
)

# Adjust coefficients with chamber diameter
foodweb_adj_Diam <- foodweb_bind %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

```{r Table of food web coefficients}
tidy_foodweb_alphas %>%
  filter(type != "Diff") %>%
  select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(Term = term, Treatment = type, Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
```

```{r Table of differences in food web coefficients, include=FALSE}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces between food-web treatments.")
```

@@

```{r Plot food-web coefficients, fig.cap="Plot of mean fitness differences between treatments and trait-fitness relationships. Asterisks denote significant differences (*P* < 0.05) between treatments."}

# Plot helpers
dodge_width <- position_dodge(width=0.5)
y_limits_foodweb_coefs <- c(min(filter(tidy_foodweb_alphas, type!="Diff")$conf.low), 
                            max(filter(tidy_foodweb_alphas, type!="Diff")$conf.high))
P_asterisk_foodweb_coefs <- 1.5
P_size <- 8
legend_foodweb_labels <- c("Complex","Simple")
point.size <- 3

# Plot mean fitness
plot_foodweb_mean_fitness <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  xlab("Food web") +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot linear trait-fitness relationaships
plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot quadratic trait-fitness relationships
plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot correlational trait-fitness relationaships
plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

## Reproduce Figure 2 in manuscript.

>>>>

---
title: "Consumer extinctions constrain phenotypic evolution in the resulting food web"
subtitle: "Supplementary information"
author: "Code author: Matthew A. Barbour"
date: "`r Sys.Date()`"
output: 
  tufte::tufte_html:
    toc: true
---

This document presents a detailed overview of the analyses presented in the main text. It highlights the essential R code used to conduct these analyses, but does not display code related to table and plot aesthetics. The underlying code for this document is provided in **reproduce_analyses.Rmd** and is available at https://github.com/mabarbour/complexity_selection.

@@

```{r color palette}
# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
# order: orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
original_color <- cbPalette[6] 
extinction_color <- cbPalette[5] 
treatment_colors <- c(original_color, extinction_color)
```

## Summary of dataset

@@

  # eliminate unknown sources of mortality
  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% 
  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% 
  mutate(Foodweb = ifelse(Treatment=="Control", "Original", "Extinction"), # rename Treatment to match presentation in manuscript
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber. I set these to 1 to permit an analysis with a binomial model.

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots)))) 
```

Below is a summary of the raw trait data for the gall midge, *Iteomyia salicisverruca*. Gall chamber diameter (**Diam**) is measured in mm, clutch size (**Clutch**) is measured as the number of chambers per gall, and oviposition preference (**Pref**) is measured as the number of chambers per 100 shoots on the plant. Note that each chamber contains one individual larva.

```{r raw trait summary}
raw_means <- gall_selection.df %>%
  transmute(Diam = chamber.diameter_mm, 
            Clutch = clutch.size_individuals, 
            Pref = oviposition.preference_individuals.per.100.shoots) %>%
  summarise_all(funs(mean))

raw_SDs <- gall_selection.df %>%
  transmute(Diam = chamber.diameter_mm, 
            Clutch = clutch.size_individuals, 
            Pref = oviposition.preference_individuals.per.100.shoots) %>%
  summarise_all(funs(sd))

data.frame(Trait = c("Diam", "Clutch", "Pref"),
           Mean = round(c(raw_means$Diam, raw_means$Clutch, raw_means$Pref), 1),
           SD = round(c(raw_SDs$Diam, raw_SDs$Clutch, raw_SDs$Pref), 1)) %>%
  knitr::kable(., caption = "Mean and SD of phenotypic traits.")
```

Clutch size and oviposition preference were not normally distributed, so we log and square-root transformed these traits, respectively.

```{r transformed trait summary}
trans_means <- gall_selection.df %>%
  transmute(log.Clutch = log(clutch.size_individuals), 
            sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots)) %>%
  summarise_all(funs(mean))

trans_SDs <- gall_selection.df %>%
  transmute(log.Clutch = log(clutch.size_individuals), 
            sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots)) %>%
  summarise_all(funs(sd))

data.frame(Trait = c("log.Clutch", "sqrt.Pref"),
           Mean = round(c(trans_means$log.Clutch, trans_means$sqrt.Pref), 1),
           SD = round(c(trans_SDs$log.Clutch, trans_SDs$sqrt.Pref), 1)) %>%
  knitr::kable(., caption = "Mean and SD of transformed phenotypic traits.")
```

For our subsequent analyses, we scaled each phenotypic trait (mean = 0, SD = 1) so that estimates of selection surfaces and gradients were comparable between traits and with traits in other studies. Below, we show a random subset of the data used in our subsequent analyses.

```{r illustrate data used in analyses}
set.seed(34)
sample_n(gall_selection.df, size = 10) %>%
  select(Foodweb, Genotype, Plant_Position, Gall_Number, Gall_ID, gall_survival, sc.Diam, sc.log.Clutch, sc.sqrt.Pref) %>%
  mutate(sc.Diam = round(sc.Diam, 2), sc.log.Clutch = round(sc.log.Clutch, 2), sc.sqrt.Pref = round(sc.sqrt.Pref, 2)) %>%
  knitr::kable(., caption = "Random sample of 10 data points used for our analyses.")
```

- **Foodweb** = food-web treatment (Original or Extinction)
- **Genotype** = plant genotype ID (n = `r length(unique(gall_selection.df$Genotype))`)
- **Plant_Position** = plant ID (n = `r length(unique(gall_selection.df$Plant_Position))`)
- **Gall_Number** = multi-chambered gall ID (n = `r length(unique(gall_selection.df$Gall_Number))`)
- **Gall_ID** = individual chamber ID (n = `r length(unique(gall_selection.df$Gall_ID))`)
- **gall_survival** = measure of larval fitness (0 = dead; 1 = survived to pupation)
- **sc.Diam** = scaled chamber diameter
- **sc.log.Clutch** = scaled logarithm of clutch size
- **sc.sqrt.Pref** = scaled square-root of oviposition preference

@@

We used graphical checks to evaluate whether our transformations resulted in traits with a multivariate normal distribution. The histograms below show that our transformations resulted in approximately normal distributions for each phenotypic trait.

Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line, suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
```

@@

## Selection surfaces for the gall midge: food-web treatments

We wrote the generalized linear mixed-effects model (GLMM) in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival. The resulting estimates and confidence intervals are useful for determining whether selection surfaces differ from zero, but not whether they differ between food-web treatments. In the main text, we discuss why we do not put much stock in differences in the magnitude of selection between food-web treatments (last paragraph of **Quantifying the Adaptive Landscape**), and therefore do not present these calculations.

@@

We then used parametric bootstrapping (n = 1000) to calculate 95% confidence intervals of selection surfaces.

```{r Bootstrap food-web model, cache=TRUE, echo=TRUE}
n_boots_analysis <- 1000

boot_foodweb_model <- bootMer(
  x = foodweb_model, 
  FUN = fixef, 
  nsim = n_boots_analysis, 
  parallel="multicore", ncpus=32, seed=34)
```

In order to reliably estimate linear relationships, we removed all higher-order terms from the model [(Stinchcombe et al. 2008)](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x),

@@

and refit using parametric bootstrapping.

```{r Bootstrap linear food-web model, cache=TRUE, echo=TRUE}
boot_linear_foodweb_model <- bootMer(
  x = linear_foodweb_model, 
  FUN = fixef, 
  nsim = n_boots_analysis, 
  parallel="multicore", ncpus=32, seed=34)
```

Chamber diameter, but not the other phenotypes, could be influenced by parasitism itself rather than being under natural selection. To estimate this potential bias, we subset our data to only include multi-chambered galls where there was variability in larval survival. We then fit a reduced model to estimate the bias in selection surfaces of chamber diameter in each food-web treatment.

@@

```{r biased foodweb table}
# Print table
biased_foodweb_confint %>%
  #select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebOriginal:sc.Diam","FoodwebExtinction:sc.Diam")) %>%
  transmute(Term = term, Estimate = round(estimate, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Estimates of bias in selection surface of chamber diameter in each food-web treatment.")
```

We then gathered bootstrapped estimates from both models, only retaining nonlinear terms from the full model,

```{r Gather food-web alphas, echo=TRUE}
foodweb_bind <- bind_cols(
  as_tibble(boot_linear_foodweb_model$t),
  # only retain nonlinear coefficients from full model
  select(as_tibble(boot_foodweb_model$t), `FoodwebExtinction:I(sc.Diam^2)`:`FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) 
)
```

and subtracted the bias in chamber diameter to better approximate its selection surface.

```{r Adjust food-web alphas for chamber diameter, echo=TRUE}
foodweb_adj_Diam <- foodweb_bind %>%
  mutate(`FoodwebOriginal:sc.Diam` = `FoodwebOriginal:sc.Diam` - fixef(biased_foodweb_model)["FoodwebOriginal:sc.Diam"],
         `FoodwebExtinction:sc.Diam` = `FoodwebExtinction:sc.Diam` - fixef(biased_foodweb_model)["FoodwebExtinction:sc.Diam"])
```

We then summarize these bootstrapped estimates and 95% confidence intervals as a table.

```{r Tidy food-web alphas}

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  mutate(`FoodwebExtinction:(Intercept)`=inverse_logit(FoodwebExtinction), `FoodwebOriginal:(Intercept)`=inverse_logit(FoodwebOriginal)) %>% # logit transform to make intercept interpretable as a probability
  select(-FoodwebExtinction, -FoodwebOriginal) %>% # translated into (Intercept) terms
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebExtinction:(Intercept)` - `FoodwebOriginal:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

```{r Table of food web coefficients}
tidy_foodweb_alphas %>%
  filter(type != "Diff") %>%
  #select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
  arrange(desc(Term)) %>%
 knitr::kable(., caption = "Table of estimates for larval survival and selection surfaces in each food-web treatment.")
```

```{r Table of differences in food web coefficients, include=FALSE}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  #select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces for gall midges between food-web treatments.")
```

@@

```{r Plot food-web coefficients, fig.cap="Plot of larval survival and selection surfaces in each food-web treatment."}
## Note that we do not focus on differences between treatments.

# Plot helpers
dodge_width <- position_dodge(width=0.5)
y_limits_foodweb_coefs <- c(min(filter(tidy_foodweb_alphas, type!="Diff")$conf.low), 
                            max(filter(tidy_foodweb_alphas, type!="Diff")$conf.high))
P_asterisk_foodweb_coefs <- 1.5
P_size <- 8
legend_foodweb_labels <- c("Original","Extinction")
point.size <- 3

# Plot mean fitness
plot_foodweb_mean_fitness <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  xlab("Food web") +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot linear trait-fitness relationships
plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot quadratic selection surfaces
plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot correlational trait-fitness relationaships
plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

## Reproduce Figure 2 in main text
